### 2019-04-17 2019_csic5011/project1/project1.tex
Add files via upload

@@

>>>>

In this exercise of open peer review, please write down your comments of the \emph{reports rather than of your own team} in the following format. Be considerate and careful with a precise description, avoiding offensive language.

Deadline is 11:59pm April 16, 2019. Submit your review in plain text to the email address (\href{mailto:datascience.hw@gmail.com}{datascience.hw@gmail.com}) with Title: \underline{CSIC 5011: Project 1 Review}. Rebuttal is open afterwards.

@@

\section*{Rebuttal}
The rebuttal period starts from now, till 11:59pm April 21, 2019. Restrict the number of characters of your rebuttal within {\bf{5,000}}. Submit your rebuttal in PLAIN TEXT or word DOC format to the email address (\href{mailto:datascience.hw@gmail.com}{datascience.hw@gmail.com}) with Title: \underline{CSIC 5011: Project 1 Rebuttal}.

The following tips of rebuttal might be helpful for you to follow:

1. The main aim of the rebuttal is to answer any specific questions that the reviewers might have raised, or to clarify any misunderstanding of the technical content of the paper.

2. Keep your rebuttal short, to-the-point, and specific. In our experience, such rebuttals have the maximum impact.

3. Always be polite and professional. Refrain from name calling or rude comments, especially in response to negative reviews.

4. Highlight the changes in your manuscripts had you made a simple revision.
